Robotic Cart System

### 2021-05-10 parts/30-implementation.tex
Updated chapter labeling

%======================================================================
\chapter{Implementation}
\label{ch: Chapter5}
%======================================================================

@@

\vspace*{12pt}
\noindent
The reflector array assembly from Chapter \ref{ch: Chapter3} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket. This bracket was then attached to the chassis using bolts. Another feature of this bracket is that it had a stop block built into the top of it to automatically zero the reflector array when the robot starts up.

@@

In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in Chapter \ref{ch: Chapter4}. There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.

@@

\vspace*{12pt}
\noindent
First, a model of the Budget Bot chassis was created in CoppeliaSim. The model is shown in Fig. \ref{fig:budgetBotModel}. The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics. Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch:coppSimModeling}. Although \autoref{ch:coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.

@@

\vspace*{12pt}
\noindent
MATLAB code was written to control the simulation. The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07. This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{sec:navAlgo}). An image of the simulation is shown in Fig. \ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/coppSimExample.png}
    \caption{CoppeliaSim Simulation}
    \label{fig:coppSimExample}
\end{figure}

>>>>

%======================================================================
\chapter{Implementation}
\label{ch: implementation}
%======================================================================

@@

\vspace*{12pt}
\noindent
The reflector array assembly from \autoref{sec:customReflector} was mounted on a stepper motor that was then attached to the robot chassis using a 3D printed bracket. This bracket was then attached to the chassis using bolts. Another feature of this bracket is that it had a stop block built into the top of it to automatically zero the reflector array when the robot starts up.

@@

In this project after we had the Robotic Cart, Remote Target, and a code base to handle the specifics we started testing different variants of our algorithm explained in \autoref{sec:locAndNavAlgos}. There were two main types of variants we put together, one type the stepper motor is locked preventing the reflector from turning and in the other we use the stepper motor to sweep through a set of angles.

@@

\vspace*{12pt}
\noindent
First, a model of the Budget Bot chassis was created in CoppeliaSim. The model is shown in Fig. \ref{fig:budgetBotModel}. The model was designed with the same dimensions as the physical chassis to accurately simulate the robot kinematics. Details on modeling a robot chassis in CoppeliaSim can be found in \autoref{ch: coppSimModeling}. Although \autoref{ch: coppSimModeling} explains the modeling of a robot chassis that is different than the Budget Bot chassis, the concepts are the same for modeling any robot chassis.

@@

\vspace*{12pt}
\noindent
MATLAB code was written to control the simulation. The actual distance between the robot and the remote was measured, then random noise was added with a mean of 0 and a standard deviation of 0.07. This noisy measurement was then used in the navigation algorithm to determine how to drive the robot (see \autoref{subsec:navAlgo}). An image of the simulation is shown in Fig. \ref{fig:coppSimExample}, where the blue sphere represents the remote, and the green dot represents the target point.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/img/coppSimExample.png}
    \caption{CoppeliaSim Simulation}
    \label{fig:coppSimExample}
\end{figure}
